---
output:
  pdf_document: 
    fig_caption: false
    number_sections: true
params:
  report.name: !r as.character("")
  reviewer: !r as.character("")
  approver: !r as.character("")
  data: !r as.character("")
  variance.data: !r as.character("")
  exposure: !r as.character("")
  model: !r as.character("")
  observed: !r as.character("")
  clm.count: !r as.character("")
header-includes:
  - \usepackage[T1]{fontenc}
  - \usepackage{lmodern}
  - \usepackage{hyperref}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyfoot[C]{CONFIDENTIAL}
  - \fancyfoot[LE,RO]{\thepage}
  - \lhead{\includegraphics[width=1cm]{TDlogo.png}}
---



\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} 

\center % Center everything on the page

%----------------------------------------------------------------------------------------
%   HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\LARGE TD Insurance}\\[1.5cm] 
\textsc{\Large Model Monitoring}\\[0.5cm] 
\textsc{\large CONFIDENTIAL}\\[0.5cm] 

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
{ \huge \bfseries `r gsub('_',' ',params$report.name)`}\\[0.4cm] 
\HRule \\[1.5cm]

%----------------------------------------------------------------------------------------
%   AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Reviewer:}\\
`r params$reviewer`
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Approver:} \\
`r params$approver`
\end{flushright}
\end{minipage}\\[2cm]



%----------------------------------------------------------------------------------------
%   DATE SECTION
%----------------------------------------------------------------------------------------

{\large \today}\\[2cm] 

%----------------------------------------------------------------------------------------
%   LOGO SECTION
%----------------------------------------------------------------------------------------

\includegraphics[width=6cm,height=6cm]{TDlogo.png}\\[1cm] 

%----------------------------------------------------------------------------------------

\vfill % Fill the rest of the page with whitespace

\end{titlepage}



%----------------------------------------------------------------------------------------
%   MAIN REPORT SECTION
%----------------------------------------------------------------------------------------


\renewcommand*{\LayoutTextField}[2]{\makebox[10em][l]{#1: }%
  \raisebox{\baselineskip}{\raisebox{-\height}{#2}}}


# Data 

## Description of Data
\begin{Form}
\TextField[name=MonitoringData, multiline=true, align=0, width=400pt, height=3\baselineskip]{Monitoring Data}\vskip1ex
\TextField[name=VarianceData,   multiline=true, align=0, width=400pt, height=3\baselineskip]{Variance Data}
\end{Form}

\renewcommand*{\LayoutTextField}[2]{\makebox[0em][l]{#1: }%
  \raisebox{\baselineskip}{\raisebox{-\height}{#2}}}

## Data filtering

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
X<-TDTools::Plot.Data(DATA = params$data,
                      VARIANCE.DATA = params$variance.data,
                      NAMES = list(MODELS    = params$model,
                                   OBSERVED  = params$observed,
                                   CLM.COUNT = params$clm.count,
                                   EXPOSURE  = params$exposure,
                                   VARIABLE  = params$model),
                      MODE = "ALL",
                      EVAL.VARIANCE = T,
                      SPLIT.VARIANCE = F,
                      N.BKTS = 20)
```

Filtering comments
\begin{center}
\begin{Form}
\TextField[name=FilterComments, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}

\newpage

# Model Overview

```{r,data,echo=FALSE,message=FALSE}

options(xtable.comment = FALSE)

Y<-data.frame(TDTools::Deviation.Chart(X,DATA.ONLY = TRUE))
colnames(Y)[2:3]<-c("%Error","Exposure")
Y$Percentile<-as.numeric(Y$N/20)

Y<- Y[Y$Percentile %in% c(0.05,0.5,0.95), 
      c("Exposure","%Error","Error_2SD","Error_3SD")]

Y$Broken_2SD = ""
Y$Broken_2SD[Y$`%Error` > Y$Error_2SD] = "X"
Y$Broken_3SD = ""
Y$Broken_3SD[Y$`%Error` > Y$Error_3SD] = "X"

Y$Error_2SD = NULL
Y$Error_3SD = NULL

Y$`%Error` = paste0(formatC(100 * Y$`%Error`, format = "f", digits = 2), "%")

colnames(Y) <- c("Exposure", "% Error", "2sd Threshold Broken", "3sd Threshold Broken")

rownames(Y) <- NULL

TBL <- xtable::xtable(Y, digits = 2, align = rep("c",5))

```

`r TBL`

Reviewer comments \& conclusions
\begin{center}
\begin{Form}
\TextField[name=ModelComments, multiline=true, align=0, width=400pt, height=15\baselineskip]{ }
\end{Form}
\end{center}




\newpage


# Model Charts

##  Predicted vs. Observed Quantile Chart

![](`r TDTools::PvO.Chart(X,AS.PDF = T)`)
\begin{center}
\begin{Form}
\TextField[name=PvOComment, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}


\newpage
## Discrepancy Chart

![](`r TDTools::Discrepancy.Chart(X, AS.PDF = T)`)
\begin{center}
\begin{Form}
\TextField[name=DiscComment, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}


\newpage
## Deviation (Error) Chart

![](`r TDTools::Deviation.Chart(X,AS.PDF =T)`)
\begin{center}
\begin{Form}
\TextField[name=DevComment, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}

\newpage
## Lorenz Curve

![](`r TDTools::Plot.Lorenz(DATA = params$data,
                     NAMES = list(MODELS   = params$model,
                                  OBSERVED = params$observed,
                                  EXPOSURE = params$exposure),
                     N.BKTS = 100,
                     DATA.ONLY = F,
                     AS.PDF=T)`)

\begin{center}          
\begin{Form}
\TextField[name=LorenzComment, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}




